SRG operator evolution

### 2019-06-03 Notes/SRG_operator_evolution/srg_operator_evolution.tex
Re-generated SRG-evolved potential figures from srg_operator_evolution_figures.ipynb
Made a minor change with the SRG generator label. Also had to had the figures to the Figures directory within the SRG_operator_evolution notes folder.

Results on SRG-evolved operators from several NN potentials:
\\
-- How operators evolve from band- and block-diagonal SRG transformations.
\\
-- Operator evolution for different potentials (regulators, chiral order, etc.)

@@

Brief description of how to make $U(s)$.
\\

@@

%------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------
\subsection{Momentum distribution function: $\phi^2$}
\label{sec:momentum_dist_funcs}

We diagonalize the Hamiltonian for eigenvectors $\phi_{\alpha}$. In the $^{3}S_1$-$^{3}D_1$ coupled channel, the S-component is given by $\phi_{\alpha}[:N]$ and the D-component by $\phi_{\alpha}[N:]$ where $N$ is the length of the momentum mesh. Then the momentum distribution is given by,

\begin{eqnarray}
	\label{eq:momentum_distribution}
	|\phi(k)|^2 = |\phi_{\alpha}[:N]|^2 + |\phi_{\alpha}[N:]|^2.
\end{eqnarray}

This satisfies the normalization condition $\sum_{i=1}^N |\phi(k_i)|^2 = 1$, implying that the factor $k^2 dk$ (or in the discrete case $k_i^2 w_i$) is factored into the wave function. For mesh-independent figures, divide by $k_i^2 w_i$.

@@

\textcolor{red}{Add takeaways for these figures.}

@@

@@

\textcolor{red}{Add takeaways for these figures.}

@@

@@

@@

\textcolor{red}{Add takeaways for these figures.}

>>>>

Results on SRG-evolved operators from several NN potentials.
\\
-- How operators evolve from band- and block-diagonal SRG transformations.
\\
-- Operator evolution for different potentials (regulators, chiral order, etc.)

@@

@@

%------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------
\subsection{Momentum distribution function: $\phi^2(k)$}
\label{sec:momentum_dist_funcs}

We diagonalize the Hamiltonian for eigenvectors $\psi_{\alpha}$. In the $^{3}S_1$-$^{3}D_1$ coupled channel, the S-component is given by $\psi_{\alpha}[:N]$ and the D-component by $\psi_{\alpha}[N:]$ where $N$ is the length of the momentum mesh. Then the momentum distribution of the state $\alpha$ is given by,

\begin{eqnarray}
	\label{eq:momentum_distribution}
	|\phi_{\alpha}(k)|^2 = |\psi_{\alpha}[:N]|^2 + |\psi_{\alpha}[N:]|^2.
\end{eqnarray}

This satisfies the normalization condition $\sum_{i=1}^N |\phi(k_i)|^2 = 1$, implying that the factor $k^2 dk$ (or in the discrete case, $k_i^2 w_i$) is factored into the wave function. For mesh-independent figures, divide by $k_i^2 w_i$.

@@

Non-local potential from \cite{Entem:2003ft}.

\begin{figure}[H]
	\centering
	\subfloat[]{%
	\includegraphics[clip,width=0.9\columnwidth]{potential_contours_kvnn10_3S1_Wegner}%
	}

	\subfloat[]{%
	\includegraphics[clip,width=0.9\columnwidth]{potential_contours_kvnn10_3S1_Block-diag2,00}%
	}

	\subfloat[]{%
	\includegraphics[clip,width=0.9\columnwidth]{potential_contours_kvnn10_3S1_Block-diag3,00}%
	}
	\caption{Caption.}
	\label{potential_contours_kvnn10_3S1}
\end{figure}

@@

-- The top row of Fig.~\ref{momentum_projection_contours_q3,00_kvnn10} should match the top row in Fig. 4 of \cite{Anderson:2010aq}.
-- Smeared delta function comment.
-- Compared block-diagonal to Wegner.
-- Another note about block-diagonal.

@@

\textcolor{red}{Add takeaways for these figures.} Semi-local potentials from \cite{Reinert:2017usi}.

@@

\begin{figure}[H]
	\centering
	\subfloat[]{%
	\includegraphics[clip,width=0.9\columnwidth]{potential_contours_kvnn106_3S1_Wegner}%
	}

	\subfloat[]{%
	\includegraphics[clip,width=0.9\columnwidth]{potential_contours_kvnn106_3S1_Block-diag2,00}%
	}
	\caption{Caption.}
	\label{potential_contours_kvnn106_3S1}
\end{figure}

\begin{figure}[H]
	\centering
	\subfloat[]{%
	\includegraphics[clip,width=0.9\columnwidth]{potential_contours_kvnn107_3S1_Wegner}%
	}

	\subfloat[]{%
	\includegraphics[clip,width=0.9\columnwidth]{potential_contours_kvnn107_3S1_Block-diag2,00}%
	}
	\caption{Caption.}
	\label{potential_contours_kvnn111_3S1}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\subfloat[]{%
	\includegraphics[clip,width=0.9\columnwidth]{potential_contours_kvnn111_3S1_Wegner}%
	}

	\subfloat[]{%
	\includegraphics[clip,width=0.9\columnwidth]{potential_contours_kvnn111_3S1_Block-diag2,00}%
	}
	\caption{Caption.}
	\label{potential_contours_kvnn111_3S1}
\end{figure}

\begin{figure}[H]
	\centering
	\subfloat[]{%
	\includegraphics[clip,width=0.9\columnwidth]{potential_contours_kvnn112_3S1_Wegner}%
	}

	\subfloat[]{%
	\includegraphics[clip,width=0.9\columnwidth]{potential_contours_kvnn112_3S1_Block-diag2,00}%
	}
	\caption{Caption.}
	\label{potential_contours_kvnn112_3S1}
\end{figure}

@@

\textcolor{red}{Add takeaways for these figures.} Local potentials from \cite{Gezerlis:2014zia}.

\begin{figure}[H]
	\centering
	\subfloat[]{%
	\includegraphics[clip,width=0.9\columnwidth]{potential_contours_kvnn222_3S1_Wegner}%
	}

	\subfloat[]{%
	\includegraphics[clip,width=0.9\columnwidth]{potential_contours_kvnn222_3S1_Block-diag2,00}%
	}

	\subfloat[]{%
	\includegraphics[clip,width=0.9\columnwidth]{potential_contours_kvnn222_3S1_Block-diag3,00}%
	}
	\caption{Caption.}
	\label{potential_contours_kvnn222_3S1}
\end{figure}

\begin{figure}[H]
	\centering
	\subfloat[]{%
	\includegraphics[clip,width=0.9\columnwidth]{potential_contours_kvnn224_3S1_Wegner}%
	}

	\subfloat[]{%
	\includegraphics[clip,width=0.9\columnwidth]{potential_contours_kvnn224_3S1_Block-diag2,00}%
	}
	\caption{Caption.}
	\label{potential_contours_kvnn224_3S1}
\end{figure}
